Appendix for 'Framing Effects in the Wild

### 2022-09-19 paper/appendix.Rmd
Add descriptives DVs

GroupedDistPlot()

@@

@@

### AfD Scalometer

@@

@@

## Bild Readership

>>>>

GroupedDistPlot("1130_clean",
                header = "Distribution of Immigration Attitudes")

@@

GroupedDistPlot("1210_clean",
                header = "Distribution of Integration Attitudes")

@@

GroupedDistPlot("mip_mig",
                header = "Mention of Migration as Most Important Problem")

### AfD Scalometer (430i in GLES)

@@

GroupedDistPlot("430i_clean",
                header = "Distribution of Attitude Towards AfD")

@@

GroupedDistPlot("2880h_clean",
                header = "Distribution of Attitude towards Fighting Crime")
